Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
pf <- read.csv('pseudo_facebook.tsv', sep = '\t')
qplot(x = age, y = friend_count, data = pf)

```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha=1/20, position = position_jitter(h = 0)) + 
  xlim(13,90) + 
  coord_trans(y = 'sqrt')
```

***

### Overplotting
Notes:

```{r Overplotting}

```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}

```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x = age, y = friendships_initiated), data = pf) +
  geom_point(alpha=1/10, position = position_jitter(h = 0)) + 
  xlim(13, 90) + 
  coord_trans(y = 'sqrt')
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
age_groups <- group_by(pf, age_with_months) 
pf.fc_by_age_months <- summarise(age_groups, 
                                                    friend_count_mean = mean(friend_count), 
                                                    friend_count_median = median(friend_count), 
                                                    n = n()) 
pf.fc_by_age_months <- arrange(pf.fc_by_age_months, age_with_months) 

head(pf.fc_by_age_months)

```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(y = friend_count_mean, x = age_with_months), data = subset(pf.fc_by_age_months, age_with_months < 71) ) +
  geom_line() + 
  geom_smooth()

```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha=1/20, position = position_jitter(h = 0), color = 'orange') + 
  #xlim(13,90) + 
  #coord_trans(y = 'sqrt') + 
  coord_cartesian(xlim = c(13,70), ylim = c(0, 1000)) + 
  geom_line(stat = 'summary', fun.y = mean) + 
  geom_line(stat = 'summary', fun.y= quantile, fun.args = list(probs =.1), linetype = 2, color  = 'blue') + 
  geom_line(stat = 'summary', fun.y= quantile, fun.args = list(probs =.5), color  = 'blue') + 
  geom_line(stat = 'summary', fun.y= quantile, fun.args = list(probs =.9), linetype = 2, color  = 'blue')

```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor.test(pf$age, pf$friend_count)
with(pf, cor.test(age, friend_count))

```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with( subset(pf, age <= 70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
ggplot(aes(y = likes_received, x = www_likes_received), data = pf) + 
  geom_point() +
  xlim(0, quantile(pf$www_likes_received, 0.95)) + 
  ylim(0, quantile(pf$likes_received, 0.95)) + 
  geom_smooth(method = 'lm', color = 'red')
  
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
cor.test(pf$www_likes_received, pf$likes_received)
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
data(Mitchell)
summary(Mitchell)
```

Create your plot!

```{r Temp vs Month}
ggplot(aes(x=Month, y = Temp), data = Mitchell) + geom_point()
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
cor(Mitchell$Temp, Mitchell$Month)

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
ggplot(aes(x=Month%%12, y = Temp), data = Mitchell) + geom_point() + 
  scale_x_continuous(breaks = seq(0,203, 12))

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
pf$age_with_months <- pf$age  + (1- pf$dob_month/12)
```

***

### Age with Months Means

```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

